---
title: "ACIC_Track2_Jacques_Merge"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r. library}
library(tidyverse)
```

```{r, data}
setwd("C:/Users/ajacques/OneDrive - RAND Corporation/R_Practice/ACIC Data Challenge/ACIC Edited or Merged Data/ACIC Track2")
practice_track2 <- read.csv("acic_practice_0001.csv")
practice_year_track2 <- read.csv("acic_practice_year_0001.csv")
track2_full_df <- merge(practice_track2, practice_year_track2, by = "id.practice")
```

# Notes on 22 March 2022 Meeting 
1. Data Propensity Score 
2. Predicting the Outcome (Outcome Function)
  Superlearner, (Ensemble of methods for predicting outcomes)
  TMLE, Bart, Entropy Balancing, tree based models, GBM
3. Data Visualization 
  Leading to modeling 
  Visualization of Estimates 

Put into estimation, put a penalty on the outcome model. Provider structure to regualize around ground mean in the same away.....
Regular out sized model and use propensity score, intercept for each provider with expectation zero. ---> Only question for track 1. Consider something that is fully interactive for the provider, each covariance changes with provider

Treatment is the provider level 

Summarize patient information then analyze in that direction. Track 2 does this already kinda? 
Track 2 is easier to handle... 

test_type